Supernova Host Galaxies in the Dark Energy Survey: \\ II. Rapidly Evolving Transients

### 2020-01-09 RET_Hosts.tex

\newcommand{\comment}[1]{\textbf{[#1]}} %comments

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%This if a fix from https://tex.stackexchange.com/questions/249579/pdfendlink-ended-up-in-different-nesting-level-than-pdfstartlink-error-with/249743#249743 to sort hyperref breaking in pdfendlink when a reference spills over a page
%\usepackage{etoolbox}
%\makeatletter
%\patchcmd\@combinedblfloats{\box\@outputbox}{\unvbox\@outputbox}{}{%
%  \errmessage{\noexpand\@combinedblfloats could not be patched}%
%}%
%\makeatother
%
%\defcitealias{Smith2019}{S19}
%\defcitealias{Kelly2012}{KK12}
%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

@@

% Enter the current year, for the copyright statements etc.
\pubyear{2019}
% These dates will be filled out by the publisher

@@

In the standard paradigm of stellar evolution, stars with a zero-age main sequence (ZAMS) mass above $8M_{\sun}$ are believed to explode as a result of a catastrophic collapse of their iron cores and are known as core-collapse supernovae (CCSNe). Since the turn of the century, observations of CCSNe have been supplemented by two rarer, more exotic transient classes. Long duration gamma-ray bursts (LGRBs), although first discovered in the 1960s \citep{Klebesadel1973} were only unequivocally linked to collapsing massive stars their associations with broad-lined type Ic SNe \citep{Galama1998,Hjorth2003}. Thought to be caused by accretion onto a newly-formed black hole at the centre of a collapsing, rapidly-rotating massive star \citep[][e.g.]{Woosley1993,Woosley2006a,Woosley2006b}, LGRBs comprise roughly $1\%$ of all SN Ic, themselves making up only 15\% of all CCSNe \citep{Kelly2012,Graham2016}.    and are roughly $10^4$ times rarer than  are thought and superluminous supernovae (SLSNe; e.g. \citealt{Quimby2011, Gal-Yam2012})

\section{Observations\label{sec:obs}}

Normally the next section describes the techniques the authors used.
It is frequently split into subsections, such as Section~\ref{sec:maths} below.

@@

\section{Analysis and results}
\label{sec:analysis} % used for referring to this section from elsewhere

>>>>

\newcommand{\comment}[1]{\textbf{[#1]}} %comments
\defcitealias{Pursiainen2018}{P18}
\defcitealias{Pursiainen2020}{P20}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%This if a fix from https://tex.stackexchange.com/questions/249579/pdfendlink-ended-up-in-different-nesting-level-than-pdfstartlink-error-with/249743#249743 to sort hyperref breaking in pdfendlink when a reference spills over a page
%\usepackage{etoolbox}
%\makeatletter
%\patchcmd\@combinedblfloats{\box\@outputbox}{\unvbox\@outputbox}{}{%
%  \errmessage{\noexpand\@combinedblfloats could not be patched}%
%}%
%\makeatother
%
%\defcitealias{Smith2019}{S19}
%\defcitealias{Kelly2012}{KK12}
%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

@@

% Enter the current year, for the copyright statements etc.
\pubyear{2020}
% These dates will be filled out by the publisher

@@

In the standard paradigm of stellar evolution, stars with a zero-age main sequence (ZAMS) mass above $8M_{\sun}$ are believed to explode as a result of a catastrophic collapse of their iron cores and are known as core-collapse supernovae (CCSNe). Since the turn of the century, observations of CCSNe have been supplemented by two rarer, more exotic transient classes. Long duration gamma-ray bursts (LGRBs), although first discovered in the 1960s \citep{Klebesadel1973} were only unequivocally linked to collapsing massive stars their associations with broad-lined type Ic SNe \citep{Galama1998,Hjorth2003}. Thought to be caused by accretion onto a newly-formed black hole at the centre of a collapsing, rapidly-rotating massive star \citep[][e.g.]{Woosley1993,Woosley2006a,Woosley2006b}, LGRBs comprise roughly $1\%$ of all SN Ic, themselves making up only 15\% of all CCSNe \citep{Kelly2012,Graham2016}, and are roughly $10^4$ times rarer than  are thought and superluminous supernovae (SLSNe; e.g. \citealt{Quimby2011, Gal-Yam2012})

\section{Sample selection\label{sec:sample}}

We derive our sample from the 106 RETs discovered in the 5-year DES-SN transient survey. This number expands upon the 72 of \citetalias{Pursiainen2018} and is presented in a companion work \citetalias{Pursiainen2020}. We refer to the full sample as DES RETs. In order to calculate host galaxy properties Of the 106 objects in the sample, \textbf{n} have a host galaxy detected in deep host galaxy photometry (Section \ref{sec:obs}), of which 49 have a host galaxy spectroscopic redshift. A further two have redshifts

\section{Host galaxy observations\label{sec:obs}}

@@

\section{Host galaxy properties}
\label{sec:analysis} % used for referring to this section from elsewhere
\subsection{Stellar Mass \label{subsec:res_mass}}

\subsection{Star formation rate \label{subsec:res_sfr}}

\subsection{Metallicity \label{subsec:res_metallicity}}

\section{Discussion \label{sec:disc}}

\subsection{Transient - host galaxy correlations}
